--- 
title: "MP"
author: "pqi"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
urlcolor: blue
linkcolor: magenta
citecolor: green
description: ''
---

# Welcome {-}

This *book* is a collect of study notes and thoughts during my experience switching from atomic, molecular, and optic physics to medical physics and practicing medical physics specialized in stereotactic body radiotherapy/radiosurgery, brachytherapy (high dose rate brachytherapy, intra-operative radiotherapy, Y-90 microsphere therapy, ...), and hyperthermia treatment. It is my belief that a good book should provide resources for readers to find or possibility to find the most straightfoward and clear answer to the question or chanllenge occurred to them. Therefore, I presented mixed different types of representations such as pictures, bulletin points, paragraphs, videos (links), which have given me the best understanding for specific questions, for your reference. 

```{r eval=FALSE, include=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
